Heatwaves Exacerbate Inequalities in Mental Health

### 2021-01-06 doc/temp-sentiment.tex

%\author[1, *]{Matthew Cooper}

@@

This work builds on existing work by \citep{baylis_weather_2018}. 
Consider going through our paper and using the ABT method for ensuring we are building up a logic string, arguments, why we're doing this, what it answers, etc.

Research has demonstrated strong linkages between ambient environmental conditions and mental health, with extreme temperatures more frequently associated with poorer overall mental health. Mental health is strongly associated with income with people in lower income levels frequently experiencing higher stress levels and less capable of finding help for coping with these stresses. Additionally, results from research on how people cope with environmental temperature extremes indicate that wealthier are better able to cope with heatwaves. Furthermore, previous studies examining relationships between environmental extremes and health sometimes aggregate data at scales too coarse to examine whether income may be an ameliorating factor. Yet we know relatively little about the interaction between temperature, mental health and income. This research examines the interactions between these three using relatively fine-scale, publicly available data. This study expands on existing temperature and sentiment - one measure of mental health - research by examining finer-scale data and incorporating income data to examine correlations between extreme temperatures and sentiment.

\section{Background}

@@

@@

Building on previous findings from Baylis and others, we hypothesize that local ambient weather conditions have a strong connection how people are feeling as expressed in the sentiment of text messages posted on Twitter [H1]. Second, we hypothesize that the weather-sentiment link will be stronger in low-income areas. That is to say, people in lower income areas will be have lower sentiment scores than those in wealthier areas. [H2]. Third, we hypothesize that people living in areas with less impervious surfaces and more vegetative tree cover will exhibit higher sentiment scores [H3].

>>>>

%\author[1, *]{Matthew Cooper}
%\author[]{Jeremiah Osborne-Gowey}
%\author[]{Zheng Liu}
%\author[]{Jie Liu}
%\author[]{Portia Adade Williams}
%\author[]{Aaron Schwartz}
%\author[]{Patrick Baylis}

@@

This work builds on existing work by \citep{baylis_weather_2018}.

%Intro Paragraph
Research has demonstrated strong linkages between ambient environmental conditions and mental health, with extreme temperatures more frequently associated with poorer overall mental health. Mental health is strongly associated with income with people in lower income levels frequently experiencing higher stress levels and less capable of finding help for coping with these stresses. Additionally, results from research on how people cope with environmental temperature extremes indicate that wealthier are better able to cope with heatwaves. Furthermore, previous studies examining relationships between environmental extremes and health sometimes aggregate data at scales too coarse to examine whether income may be an ameliorating factor. Yet we know relatively little about the interaction between temperature, mental health and income. This research examines the interactions between these three using relatively fine-scale, publicly available data. This study expands on existing temperature and sentiment - one measure of mental health - research by examining finer-scale data and incorporating income data to examine correlations between extreme temperatures and sentiment.

@@

\section{Background}
% Heatwaves are known to worsen mental health
https://doi.org/10.1016/j.puhe.2018.06.008 (review study - will have more to cite)
https://www.nature.com/articles/s41558-018-0222-x
https://ehp.niehs.nih.gov/doi/full/10.1289/ehp.11339

% AND mental health is strongly associated with income
https://jamanetwork.com/journals/jamapsychiatry/fullarticle/211213
https://doi.org/10.1002/9781118410868.wbehibs570
https://www.sciencedirect.com/science/article/abs/pii/S027795362030527X
https://www.sciencedirect.com/science/article/pii/S2468266717300117
https://doi.org/10.1016/S2468-2667(17)30011-7
https://link.springer.com/article/10.1007/s00127-017-1370-4

% AND wealthier better able to cope with heatwaves 
https://www.nature.com/articles/nclimate3253
https://www.sciencedirect.com/science/article/abs/pii/S0378778818321327

% BUT we know little about the interaction between heatwaves, mental health and income

% THEREFORE: we did this really novel study.

%OTHER LEFTOVER TEXT TO MAYBE BRING IN LATER

@@

Building on previous findings from Baylis and others, we hypothesize that local ambient weather conditions have a strong connection how people are feeling as expressed in the sentiment of text messages posted on Twitter [H1]. Second, we hypothesize that the weather-sentiment link will be stronger in low-income areas. That is to say, people in lower income areas will be have lower sentiment scores than those in wealthier areas. [H2].
